Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-03-07 WRITEUP/ms.tex
remove again

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss16_gas_toomre_proj_0}
\caption{
Maps of the total gas surface density (top left), 
velocity dispersion (top right),
epicyclic frequency (bottom left), 
and Toomre $Q$ parameter (bottom right) in the $xy$-plane.
Modest smoothing has been applied to the maps. 
A divergent colormap is used for the Toomre $Q$ map to facilitate 
identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
\label{fig:Q}}
\addtocounter{figure}{-1}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss16_gas_toomre_proj_1}
\caption{Continued. Maps showing the various quantities projected on the $xz$-plane.}
\addtocounter{figure}{-1}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss16_gas_toomre_proj_2}
\caption{Continued. Maps show the various quantities projected on the $yz$-plane.}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/}
\caption{
Effective two-component Toomre Q map in the $xy$-plane.
Modest smoothing has been applied to the maps. 
A divergent colormap is used for the Toomre $Q$ map to facilitate 
identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
\label{fig:Qeff}}
% \addtocounter{figure}{-1}
\end{figure*}

>>>>

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{{\figpath/ss16_gas_toomre_proj_0_zoom_2.0_kpc}}
\caption{
Maps of the total gas surface density (top left), 
velocity dispersion (top right),
epicyclic frequency (bottom left), 
and Toomre $Q$ parameter (bottom right) in the $xy$-plane.
Modest smoothing has been applied to the maps. 
A divergent colormap is used for the Toomre $Q$ map to facilitate 
identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
\label{fig:Q}}
\addtocounter{figure}{-1}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{{\figpath/ss16_gas_toomre_proj_1_zoom_2.0_kpc.png}}
\caption{Continued. Maps showing the various quantities projected on the $xz$-plane.}
\addtocounter{figure}{-1}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{{\figpath/ss16_gas_toomre_proj_2_zoom_2.0_kpc.png}}
\caption{Continued. Maps show the various quantities projected on the $yz$-plane.}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{{\figpath/ss16_star_toomre_proj_0_zoom_2.0_kpc.png}}
\caption{
Same as \Fig{Q} but for the stellar component, projected in the $xy$-plane.
\label{fig:Qstar}}
% \addtocounter{figure}{-1}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{{\figpath/ss16_toomreEff_proj_0_zoom_2.0_kpc.png}}
\caption{
Effective two-component Toomre Q map in the $xy$-plane.
Modest smoothing has been applied to the maps. 
A divergent colormap is used for the Toomre $Q$ map to facilitate 
identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
\label{fig:Qeff}}
% \addtocounter{figure}{-1}
\end{figure*}
